For damage type listed as _/_, the weapon can deal either type of
damage for a given attack.  For a P/S weapon, the attcker can choose
to do a P or S attack. For every point of STR under Min. STR, the
attack gets -1 damage and -2 to strike/parry. STR Req is the minimum
strength required to wield the weapon. For every point of STR over the
Strength Requirement, add one point of damage to the raw roll, up to a
maximum of the MSB (Max Strength Bonus) A raw bonus is always
indicated with square brackets.  So 3D4+1 [+4] would be a normal 3D4+1
roll, with an additional 4 added to the final result. When wielding a
1-H weapon with two hands, assume the wielder has +2 STR.

\begin{description}
\item[Hands] Number of hands required to use the weapon
\item[Rec] Number of actions it takes to recover after attacking with
  the weapon.  This many actions must be spent to get the weapon ready
  for attack again.
\item[Enc] Represents the weight of the weapon.  This consumes
  Encumbrance just like armor.  Only use this when the weapon is
  actually being used.
\item[Range] the effective ``Reach'' of the weapon in feet.  If your
  target is beyond your range, you cannot strike them. You can spend
  an action to gain range on your opponent. If your target is closer
  than $1\over2$ range, then you are at -6 to strike the target.
\end{description}

\subsection{Options for Melee Weapons}
Prices listed are for basic weapons with enough durability to function
in real combat situations.  They are not showpieces or wallhangers.
However, other options are available for an extra cost:

\begin{longtable}{l|ccc}
\multicolumn{4}{c}{Options for melee weapons} \\
\hline
\endfirsthead
Exceptional Quality & +1 damage & double cost & Adds 1 to rarity \\
Master Quality & +2 damage & 10 times cost & Adds 3 to rarity \\	
Legendary Quality & +3 damage & 100 times cost & Adds 5 to rarity \\		
Vibro-edge (bladed only) & +10 AP & 5 times cost. & 	ULTRAMODERN \\
Wooden Training & $1\over2$ damage, C	& ${1\over{10}}^{th}$ cost \\
\caption{Options for mel\'{e}e weapon construction} \\
\end{longtable}


For other than normal sized weapons (mecha, etc.), all stats are
$2^{Size-1}$ normal.  This applies to strength requirement, strength
bonus, damage dice number, etc.
