Plasma weapons are designed for a specific set of modifications. These
are:

\begin{table}[htb]
\begin{center}
\begin{tabular}{lp{2.5in}l}
  \textbf{Type} & \textbf{Effect} & \textbf{Cost Factor} \\
  \hline
  \hline
  High temperature &
  Blade is hotter than normal, dealing +1 damage, can be purchased up to 3 times (each time double cost) &
  x2 \\
  Over powered field
  & The magnetic field is stronger than normal, giving a +5 STR when breaking from a lock &
  x2 \\
  High speed blade &
  The plasma weapon can be turned on in 0 actions &
  x1.5 \\
  Power burst & Once per minute the blade's power can be increased to deal +3 damage &
  x1.5\\
\end{tabular}
\caption{Plasma Weapon Modifiers}
\end{center}
\end{table}

\subsubsection{Notes: specific to Plasma Weapons}
\begin{itemize}
\item Plasma weapons are a bladeless handle (typically looks like a
  normal weapon handle or a flashlight) from which a glowing blade of
  extremely hot plasma vents forth.  The plasma is held in the shape
  of a cylinder (or blade) by a magnetic field. They take an action to
  turn on.
\item Due to the difference between using a plasma weapon verses
  normal weapons, they require the Archaic Weapons - Energy skill to
  use. Anyone can use their normal sword skill (or axe skill
  respectively) but will get a critical failure on a 4 or below
  (instead of the normal 1).
\item Plasma weapons cannot be parried by non-plasma weapons,
  likewise, they cannot parry non-plasma weapons.  Similarly, shields
  cannot block plasma weapons.  Plasma weapons can parry other plasma
  weapons, and force fields protect against them as normal If a plasma
  weapon comes in contact with another one, there is a 25\% chance the
  magnetic fields of the blades will lock together. It is easy to tell
  if combatants are locked as an extremely bright glow emanates from
  the contact point of the weapons. Getting out of a lock requires an
  action where a strength contest ensues.  If there is more than a
  difference of 8 between the two strength rolls, the lock is broken
  and the loser loses his or her next action.  If no break occurs, the
  combatants must attempt again on the next action. Either combatant
  in a lock can turn off their weapon, in which case he or she
  automatically loses the lock challenge, and gets the same negative
  as if he lost due in a STR contest.
\item One side effect of having a magnetic field around the blade, is
  that it is possible to parry projectile energy attacks (such as
  shots from a beam rifle).  Doing so the wielder is at a -8.

\end{itemize}